Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 revise/revise.tex
again, more concerns about the overstatement of fidelity.
cleaning up responses
fixes sentence in revise doc about petsc

\question The authors write:
``Moltres is devoted to previously unmatched fidelity in coupled neutronics and 
        thermal hydraulics MSR simulation.''
This is an overstatement as codes with similar degree of fidelity have been written in the past. This is the case of the tools developed in the frame of the Evol project, as well as e.g. the work from Aufiero on the coupling between OpenFOAM and Serpent (that the authors mention earlier in the introduction). The authors are required to modify this sentence based on a better bibliographical research.
\begin{solution}
        <++>
\end{solution}

@@

\question Are all equations solved on the same mesh? In this case, is this a strict requirement? Please clarify.
\begin{solution}
        This has now been clarified in the introductory text. The equations are 
        solved on a single mesh. This is enabled by the underlying MOOSE 
        framework, which also enables 'loose' coupling instead.
\end{solution}

@@

\question The proposed scaling test is very limited. Proper scaling tests would require weak and strong scaling tests, an assessment on the impact of the size of problem per core, a separate assessment of intra-node and extra-node scaling, etc. In addition, information should be provided on the employed numerical algorithms and on the parallelization strategy. The authors should either extend significantly the section, or remove it completely.
\begin{solution}
        We performed strong and weak scaling up to 768 cores separately for 
        intra-node and extra-node cases. Parallelization was implemented using 
        LibMesh library (for automatical domain decomposition) and PetSc 
        library which contains set of parallel solvers. Detailed information, 
        including results of the scalind studies, has now been added in the 
        Section 4.3 introduction.
\end{solution}

>>>>

\question The authors write:
``Moltres is devoted to previously unmatched fidelity in coupled neutronics and 
        thermal hydraulics MSR simulation.''
This is an overstatement as codes with similar degree of fidelity have been written in the past. This is the case of the tools developed in the frame of the Evol project, as well as e.g. the work from Aufiero on the coupling between OpenFOAM and Serpent (that the authors mention earlier in the introduction). The authors are required to modify this sentence based on a better bibliographical research.
\begin{solution}
        That statement has been removed and the bibliography has been enriched 
        (as discussed above).
\end{solution}

@@

\question Are all equations solved on the same mesh? In this case, is this a strict requirement? Please clarify.
\begin{solution}
        This has now been clarified in the introductory text. The equations are 
        solved on a single mesh. This is enabled by the underlying MOOSE 
        framework, which also enables `loose' coupling instead.
\end{solution}

@@

\question The proposed scaling test is very limited. Proper scaling tests would require weak and strong scaling tests, an assessment on the impact of the size of problem per core, a separate assessment of intra-node and extra-node scaling, etc. In addition, information should be provided on the employed numerical algorithms and on the parallelization strategy. The authors should either extend significantly the section, or remove it completely.
\begin{solution}
        We performed strong and weak scaling up to 768 cores separately for 
        intra-node and extra-node cases. Parallelization was implemented using 
        LibMesh library for automatic domain decomposition and PetSc 
        library for parallel solution of systems of non-linear equations. 
        Detailed information, including results of the scalind studies, has now 
        been added in the Section 4.3 introduction.
\end{solution}
